Biterm Topic Model

### 2020-07-01 btm.Rmd
Update doc, add BTM Vignette

---
title: "Biterm Topic Model"
output: github_document
author:
  - Chung-hong Chan ^[University of Mannheim]
---

@@

```{r}
require(BTM)
require(quanteda)
devtools::load_all()
trump_corpus <- corpus(trump2k)
```

@@

>>>>

@@

```{r}
require(BTM)
require(quanteda)
require(oolong)
trump_corpus <- corpus(trump2k)
```

@@

`btm_dataframe` must not be NULL.

```{r, error = TRUE}
oolong <- create_oolong(trump_btm, trump_corpus)
```

`input_corpus` must be a quanteda corpus.

```{r, error = TRUE}
oolong <- create_oolong(trump_btm, trump2k, btm_dataframe = trump_dat)
```
